Classless Java

### 2015-11-03 paper/sections/RelatedWork.tex
related work

- traits (original, variations, scala)
- mixins (original, scala)
- multiple inheritance
- expression problem
- ...

>>>>

Multiple Inheritance in Java

default methods and the paper that we found. 
traits programming in java 8.
- proposals for extending Java with traits/multiple inheritance/...

Multiple Inheritance

- traits (original, variations, scala)
- mixins (original, scala)
- multiple inheritance
- ...

ThisType/MyType/Extensibility

We are using covariant-return types to simulate some uses 
of ThisType/MyType. Only works on positive positions, whereas 
MyType is more general, as it works on any positions. Nevertheless 
our approach is still useful (for example for fluent interfaces).

- expression problem

Type-Directed Translations/Syntactic Sugar

- SugarJ

We can model certain types of language extensions with annotations 
only, but those extensions do not introduce new syntax: they 
merely do automatic code generation.

- Meta-programming techniques?

Annotations/Code Generation/Lombok

What is the difference between our work and existing annotations? 
What is it that we can do that, those annotations cannot?

Fluent Interfaces

Talk about existing libraries that use fluent interfaces (do any of 
those use any code generation to assist in the implementation?).
